Reading Notes

### 2020-09-11 1summ.tex
add title

\begin{center}
\large{\textbf{Title}} %%TODO
%\large{\textbf{ADVANCEMENT OF ORGANIC PHOTOVOLTAICS THROUGH ARTIFICIAL NEURAL NETWORKS}}
\end{center}
\begin{center}
    Jenny W. Fothergill
\end{center}
\begin{center}
    \textbf{Project Summary}
\end{center}
%\begin{center}
%\emph{Maximum of 1 page}
%\end{center}
% This should be a brief statement of the problem you plan to address.
% It should look something like an abstract.

@@

This proposal has the potential to transform the manufacturing of sustainable low-cost power generation
A coarse graining pipeline will help make multi-scale simulations more accesible and useable for others. 
This is an important step for screening potential OPV compounds.

This proposal has a the potential to transform the norms of molecular simulation.
By developing software with a focus on transferrability, reproducibility, usability, and extensibility and thinking beyond just solving a problem but thinking about how to solve the problem for the end-user we can help to change the norms in the computational sciences.
While we recognise the proposed work is challenging, we are positioned for success based on our prior work developing proofs of concept and molecular simulation on gpus.

\begin{center}
    \textbf{Broader Impacts}
\end{center}
% There are 4 kinds of broader impacts.
% 1. advance discovery and understanding while promoting teaching,
% training and learning
% 2. broaden the participation of underrepresented groups
% 3. disseminated broadly to enhance scientific and technological
% understanding
% 4. benefits of the proposed activity to society

%OPV devices reaching consistent efficacies of 15\% have the potential to create a global energy revolution.
%At this efficiency, OPV devices will surpass inorganic solar cells, and even gas and coal in terms of cost per watt of electricity generation.
%Thus, regardless of the current administration's reluctance to accept the reality of climate change, OPV devices will be seen superior to 'dirty' power production methods due to their competitive price.

Bring new students in to the software development process.
Helping to make research transferrable, reproducible, useable, and extensible. 
Writing tutorials and documentation while keep in mind principles of oftware carpentry instructor training. 
Using software dev best practices to be efficient and make sure that I'm not making code for someone else to struggle through later. 
Training/teaching undergrads.
Working as part of a team.

All code-bases will be free and open source with tutorial and documentation so that not only are they available but accessible.
By integrating what I do with other existing codebases I can help to achieve this goal.

>>>>

\begin{center}
    \large{\textbf{Advancing organic photovoltaics with infrastructure for transferable, reproducible, useable, and extensible (TRUE) multiscale models}}
%\large{\textbf{ADVANCEMENT OF ORGANIC PHOTOVOLTAICS THROUGH ARTIFICIAL NEURAL NETWORKS}}
\end{center}
\begin{center}
    Jenny W. Fothergill
\end{center}
\begin{center}
    \textbf{Project Summary}
\end{center}
%\begin{center}
%\emph{Maximum of 1 page}
%\end{center}
% This should be a brief statement of the problem you plan to address.
% It should look something like an abstract.

@@

The proposed work is original, taking a systems view of software interoperability needed to improve organic photovoltaics with molecular simulation.
Through focus on transferable, reproducible, usable, and extensible simulation infrastructure, the proposed work is positioned to transform both the manufacturing of sustainable power technologies and the norms of practice in computational materials science.
The intellectual merit of project components---coarse-graining pipelines and multiscale simulations---includes the potential to transform materials simulations adjacent to organic photovoltaics, including polymers for structural composites and molecules of biomedical interest.
The specific insight into structure-property relationships in OPV materials also has intellectual transferability to broader polymer assembly problems, and charge transport problems of interest in piezoelectric materials, induction welding of polymers, and organic electronics broadly.
PI Fothergill is positioned to be successful in the propsed work, with published expertise in quantum chemical methods applied to charge transport in organic dyes, organometallic crystals, and coarse-grained materials simulation; and as a trained Software Carpentry instructor, and open-source project contributor.
Ample computational resources are available to complete the proposed work, in the form of local HPC resources (Fry: 32 NVIDIA Pascal P100 gpus, R2: 28 P100 GPUs, Borah: ~30 GPUs coming online this year), Idaho resources (Idaho National Lab facilities: 100's of V100 GPUs) and national resources (125,000 GPU-hour allocation on XSEDE Bridges ).

\begin{center}
    \textbf{Broader Impacts}
\end{center}
% There are 4 kinds of broader impacts.
% 1. advance discovery and understanding while promoting teaching,
% training and learning
% 2. broaden the participation of underrepresented groups
% 3. disseminated broadly to enhance scientific and technological
% understanding
% 4. benefits of the proposed activity to society
%OPV devices reaching consistent efficacies of 15\% have the potential to create a global energy revolution.
%At this efficiency, OPV devices will surpass inorganic solar cells, and even gas and coal in terms of cost per watt of electricity generation.
%Thus, regardless of the current administration's reluctance to accept the reality of climate change, OPV devices will be seen superior to 'dirty' power production methods due to their competitive price.

The proposed work directly advances discovery and understanding of organic photovoltaic materials physics, molecular simulation, and scientific software development, while promoting teaching: Applying Software Carpentry pedagogical methods to tutorial development and TRUE simulations is the mechanism for simultanesouly advancing discovery while promoting teaching.
A direct consequence of applying The Carpentries' inclusivity-based pedagogical practices is that this work helps broaden participation of underrepresented groups: My own trajectory as a female in a STEM PhD program is empowered by this approach.
The products of this work---journal publications, data sets,  and open source software---are to be dissemenated free of subscription costs to users online.
By disseminating work broadly in this way, this work is positioned to have both broad impact in the application of the transferable tools we develop, and in the opportunity to influence the norms of scientific software development.
Finally, while undoubtebly aspirational, the proposed work is positioned to identify formulations of organic photovoltaics that can benefit society by significantly ameliorating global climate change.
